Photo-D with LSST: stellar photometric distances out to the edge of the Galaxy

### 2024-08-28 paper/pipeline.tex
Mario's LSDB blurbs added.

{\bf Lovro:} will here describe LSDB implementation (with Neven's help) and pipeline performance on the full TRILEGAL catalog...

LSDB = Large Survey Database

@@

One of the recent tools developed to efficiently loop across the sky patches and perform some per-patch calculations is the \href{https://lsdb.readthedocs.io/}{Large Survey Database}\footnote{https://lsdb.readthedocs.io/}.

>>>>

% {\bf Lovro:} will here describe LSDB implementation (with Neven's help) and pipeline performance on the full TRILEGAL catalog...

The scale of the dataset expected from LSST -- O(10Bn) objects -- makes this
computation challenging to perform on a single core or computer. Ideally,
one would wish to execute the computation in parallel on many (hundreds) of cores,
likely housed on a number of separate nodes. This requires a distributed
processing framework capable of orchestrating such a solution.

@@

For our work, we've adopted the \href{https://lsdb.readthedocs.io/}{\em Large Survey Database} (LSDB; \cite{2024AAS...24326109W})
framework.  LSDB is a distributed computing framework written in Python,
which enables multi-node and multi-core computation on large (PB-scale),
partitioned, catalog datasets.  It extends the concepts of the LSD toolkit
\citep{2011AAS...21743319J}
to astronomical catalogs where the distribution of objects on the sky is
very uneven -- such as is the case for Galactic star counts.  Leveraging
broadly adopted community libraries such as astropy, Pandas, and Dask, LSDB
presents a user-friendly API on which it is possible to build our pipeline.

Specifically, LSDB allows us to define a piece of computation (the PhotoD
function, written in Python) that should be executed either on every object in
the catalog, or on a per-patch basis (where the patch has a potentially
dynamically sized solid angle). For example, we compute priors for each of the 
patches (\S\ref{sec:priors}). LSDB then ensures that these functions are successfully run over the entire (arbitrarily sized) catalog. LSDB handles the data distribution and
movement between multiple nodes in the cluster, automatically handles
transient failures, and writes the output (in parallel) to another
partitioned, searchable, table.

% Using this approach, we were able to process simulated catalogs up to XX in
% size, using YY nodes, in XX wall-clock hours. Extrapolating to expectations
% for Rubin's DR1, we calculate the same cluster will be able to repeat this
% computation on real data in ZZ hours.

%One of the recent tools developed to efficiently loop across the sky patches and perform some per-patch calculations is the \href{https://lsdb.readthedocs.io/}{Large Survey Database}\footnote{https://lsdb.readthedocs.io/}.
